---
title: "sec-location"
author: "Chiyoung Ahn"
date: "November 12, 2018"
# output: html_document
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("rvest") # uncomment and run this line if rvest is not installed
# install.packages("dplyr") # uncomment and run this line if dplyr is not installed
# install.packages("stringr") # uncomment and run this line if stringr is not installed
# install.packages("ggmap") # uncomment and run this line if ggmap is not installed
library(rvest)
library(dplyr)
library(stringr)
library(ggmap)
```

## Getting location
It turns out that company addresses are not sufficient -- we need geographical locations in terms of latitude and longitude as well. One good news is that `ggmap` can handle this pretty well. Construct the following function that returns the address given an addresss string:
```{r address-to-location}
GetGeocode <- function (address) {
  geocode(address, source = "dsk") # extract geocode using Data Science Toolkit
}
```

For instance, the geocode of company `BOREALIS TECHNOLOGY CORP` from `https://www.sec.gov/cgi-bin/browse-edgar?action=getcompany&CIK=0001014767&owner=include&count=40&hidefilings=0` can be found by passing their business address:
```{r address-to-location-example}
address <- "4070 SILVER SAGE DR\nSTE 211\nCARSON CITY NV 89701"
GetGeocode(address)
```
where `lon` and `lat` indicate its longitude and latitude respectively.

### Multiple locations
Getting multiple locations can be done by using `lapply` function:
```{r addresses-to-locations}
addresses <- c("4070 SILVER SAGE DR\nSTE 211\nCARSON CITY NV 89701",
               "ONE APPLE PARK WAY\nCUPERTINO CA 95014")
locations <- lapply(addresses, GetGeocode)
print(locations)
```

`lapply` performs broadcasting a given function (second parameter) to a vector (first parameter) and returns a list, which is why it is called *l*`apply`. To extract longitudes and latitudes, one can call the followings.
```{r extract-lon-lat}
lons <- sapply(locations, "[[", "lon") # extract lon elements from a list of lists
lats <- sapply(locations, "[[", "lat") # extract lat elements from a list of lists
location.df <- data.frame(lon = lons, lat = lats)
```


## Plotting locations
```{r plot-locations}
usa.map <- map_data("state") # load USA map from ggmap
ggplot(location.df, aes(x=lon, y=lat)) + 
  borders("usa", colour="gray50", fill="white") + 
  geom_map(data=usa.map, map=usa.map,
          aes(long, lat, map_id=region),
          color="gray30", fill=NA) +
  geom_point(color="red", size=4) + 
  labs(x = "Longitude", y = "Latitude", title = "Firm locations") +
  theme_bw() 
```

TODO: it might be interesting to see location difference across industries.